A Fast Unified Model for Parsing and Sentence Understanding

### 2016-03-18 writing/hard_stack_paper/paper.tex
More typo fixes

For SPINN to be able to operate on unparsed inputs, it needs to be able to produce its own transition sequence $\mathbf t$ rather than relying on an external parser to supply is as part of the input. To do this, the model predicts $t_t$ at each step using a simple two-way softmax classifier over tracking LSTM features:
\begin{equation}
\vec{p}_{\text{t}} = \text{softmax}(W_{\text{trans}}\vec{h}_{\text{tracking}} + \vec{b}_{\text{trans}})
\end{equation}
At test time, the model uses whichever transition (i.e., \shift~or \reduce) is assigned a higher probability. The prediction function is trained to mimic the decisions of an external parser, and the decisions of this external parser are used as the inputs to the model during training. For SNLI, we use the binary Stanford PCFG Parser parses that are included with the corpus for this purpose. We did not find the technique of scheduled sampling \citep{bengio2015scheduled}, or allowing the model to use its own transition decisions in some instances at training time, to be helpful.

>>>>

For SPINN to operate on unparsed inputs, it needs to be able to produce its own transition sequence $\mathbf t$ rather than relying on an external parser to supply it as part of the input. To do this, the model predicts $t_t$ at each step using a simple two-way softmax classifier over tracking LSTM features:
\begin{equation}
\vec{p}_{\text{t}} = \text{softmax}(W_{\text{trans}}\vec{h}_{\text{tracking}} + \vec{b}_{\text{trans}})
\end{equation}
At test time, the model uses whichever transition (i.e., \shift~or \reduce) is assigned a higher probability. The prediction function is trained to mimic the decisions of an external parser, and the decisions of this external parser are used as the inputs to the model during training. For SNLI, we use the binary Stanford PCFG Parser parses that are included with the corpus for this purpose. We did not find the technique of scheduled sampling \citep{bengio2015scheduled}, or allowing the model to use its own transition decisions in some instances at training time, to be helpful.
